My Publication Title --- Single Author

### 2025-07-10 paper/quarto_aaai/paper.tex
adjusted reference to caption

\caption{\label{fig-mnist}Explanations for \emph{MNIST} for BL (top) and
CT (bottom). First column is a random factual 0. Columns 2 to 5 are
corresponding \emph{ECCo} counterfactuals in target classes 1 to 4.
Columns 6 to 10 show integrated gradients averaged over all test images
in classes 5 to 9.}

@@

We also find that CT can reduce sensitivity to immutable, protected
features and thus lead to less costly counterfactual outcomes as
illustrated in Figure~\ref{fig-poc}. In column three of
Table~\ref{tbl-main}, we impose mutability constraints on selected
features and compute the reduction in average costs of counterfactuals
associated with CT compared to the weak baseline: for synthetic
datasets, we always protect the first feature; for all real-world
tabular datasets we could identify and protect an \emph{age} variable;
for \emph{MNIST}, we protect the five top and bottom rows of digits.
Reductions in costs are overwhelmingly positive and significant of up to
nearly 60\% for \emph{GMSC}. While the estimated cost reductions for
\emph{Adult} and \emph{MNIST} are not significant,
Figure~\ref{fig-mnist} demonstrates that CT does have the expected
effect: sensitivity to protected features as proxied by integrated
gradients is drastically reduced\footnote{Additional findings for
  integrated gradients are reported in the appendix.}. In the case of
\emph{Cred}, average costs increase, likely because any potential
benefits from protecting the \emph{age} are outweighed by the increase
in costs required for greater plausibility.

>>>>

\caption{\label{fig-mnist}Explanations for \emph{MNIST} for BL (top) and
CT (bottom). First column is a random factual 0 (blue). Columns 2 to 5
are corresponding \emph{ECCo} counterfactuals in target classes 1 to 4.
Columns 6 to 10 show integrated gradients averaged over all test images
in classes 5 to 9.}

@@

We also find that CT can reduce sensitivity to immutable, protected
features and thus lead to less costly counterfactual outcomes as
illustrated in Figure~\ref{fig-poc}. In column three of
Table~\ref{tbl-main}, we impose mutability constraints on selected
features and compute the reduction in average costs of counterfactuals
associated with CT compared to the weak baseline: for synthetic
datasets, we always protect the first feature; for all real-world
tabular datasets we could identify and protect an \emph{age} variable;
for \emph{MNIST}, we protect the five top and bottom rows of digits.
Reductions in costs are overwhelmingly positive and significant of up to
nearly 60\% for \emph{GMSC}. While the estimated cost reductions for
\emph{Adult} and \emph{MNIST} are not significant,
Figure~\ref{fig-mnist} (columns 6-10) demonstrates that CT does have the
expected effect: sensitivity to protected features as per integrated
gradients is drastically reduced\footnote{Additional findings for
  integrated gradients are reported in the appendix.}. In the case of
\emph{Cred}, average costs increase, likely because any potential
benefits from protecting the \emph{age} are outweighed by the increase
in costs required for greater plausibility.
